Fine-scale Twitter Big Data Reveals Neighborhood Inequalities in Mental Health Effects of High Temperatures

### 2021-04-28 doc/temp-sentiment.tex
.

\begin{abstract}
%Limit 150 words: https://www.nature.com/nclimate/about/content
%Actually there are lots of examples of articles with > 150 words, but I think we should keep it concise
Higher temperatures associated with climate change are expected to have major impacts on human mental health.  Indeed, traditional analyses of heat and mental health outcomes using data collected by public agencies have found associations between elevated temperatures and increases in outcomes such as suicides and mental-health related hospitalizations.  However, these studies, which typically use data reported at the city or county level, have found no difference in vulnerability based on income.  We overturn this finding and show that there are stark differences in vulnerability using a novel data source: expressed sentiment in 250 million geolocated tweets, matched with prevailing weather and neighborhood socioeconomic conditions.  We find that increased temperatures worsen expressed sentiment in all areas, but that this effects is much stronger in poor and black neighborhoods.

>>>>

\begin{abstract}
%Limit 150 words: https://www.nature.com/nclimate/about/content
%Actually there are lots of examples of articles with > 150 words, but I think we should keep it concise
Higher temperatures associated with climate change are expected to have major impacts on human mental health.  Indeed, traditional analyses of heat and mental health outcomes using data collected by public agencies have found associations between elevated temperatures and increases in outcomes such as suicides and mental-health related hospitalizations.  However, these studies, which typically use data reported at the city or county level, have found no difference in vulnerability based on income.  We overturn this finding and show that there are stark differences in vulnerability using a novel data source: expressed sentiment in 250 million geolocated tweets, matched with prevailing weather as well as neighborhood economic and demographic conditions.  We find that increased temperatures worsen expressed sentiment in all areas, but that this effects is much stronger in poor and black neighborhoods.
